Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-31 doc/manuscript/manuscript.Rmd
update MCG discussion

Of particular interest in this study was testing the association between mycelial compatibility groups (MCGs) and multilocus genotypes (MLGs).
In the past MCGs have been used as a proxy for clonal lineages [@leslie1993fungal; @otto-hanson2011variation; @kohn1990mycelial; @schafer2006optimized; @kohn1995clonal; @carbone1999patterns; @lehner2015genetic]. 
When using genetic markers with MCGs, there are three basic relationship patterns, 1) One MLG to one MCG, 2) Several MLGs belong to one MCG, and 3) Several MCGs belong to one MLG, noting that 2 and 3 are not mutually exclusive.
Similar to what has been observed in other studies, our results show all three patterns (Fig. \@ref(biggraph)) [@ford1995heterokaryon; @aldrich-wolfe2015genetic; @carbone1999patterns; @attanayake2012genetic].

@jo2008reassessment; @papaioannou2014barrage; @micali2003independence;

>>>>

Of interest in this study was testing the association between mycelial compatibility groups (MCGs) and multilocus genotypes (MLGs).
In the past MCGs have been used as a proxy for clonal lineages [@leslie1993fungal; @otto-hanson2011variation; @kohn1990mycelial; @schafer2006optimized; @kohn1995clonal; @carbone1999patterns]. 
Our results do not support this hypothesis (Fig. \@ref(biggraph)).
Over the past few years, researchers have noticed inconsistencies among the relationship between MCGs and MLGs [@aldrich-wolfe2015genetic; @carbone1999patterns; @attanayake2012genetic; @lehner2015genetic]. 
Either several MCGs belong to one MLG, which could be explained by insufficient sampling of loci; several MLGs belong to one MCG, which could be explained by clonal expansion; or a mixture of both.
Some studies have shown a correlation between MCG and MLG [@aldrich-wolfe2015genetic; @carbone1999patterns; @lehner2015genetic], whereas other studies have shown no apparent correlation, even on small spatial scales [@attanayake2012genetic; @attanayake2013sclerotinia].

One long-held assumption was that MCGs (as determined via barrage reaction) represent vegetative compatibility groups (VCGs) [@schafer2006optimized; @kohn1990mycelial; @lehner2015genetic], which are known to have a genetic component [@saupe2000molecular; @hall2010evolution; @strom2016genomes].
While our results appear to contradict this assumption, our protocol for assessing MCGs utilized a different substrate for these reactions and, thus may not accurately reflect the true MCG dynamics. 
However, it has been demonstrated in several Ascomycetes---including *Neurospora crassa* [@micali2003independence], *Sclerotinia homoecarpa* [@jo2008reassessment], *Verticillium dahliae* [@papaioannou2014barrage], and *S. sclerotiorum* [@ford1995heterokaryon]---that barrage reactions are independent from stable anastomosis.
Thus, the inconsistencies in this study and other studies indicate that researchers studying *S. sclerotiorum* should not rely on MCG data derived from barrage reactions as an indicator for genetic diversity.
